---
title: "BQ Patent Exploration"
output: github_document
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = TRUE
)
```

## About

Google Patents Public Datasets is a collection BigQuery database tables from government, research and private companies for conducting statistical analysis of patent data.

https://cloud.google.com/blog/products/gcp/google-patents-public-datasets-connecting-public-paid-and-private-patent-data

This notebook provides an overview about the structure of the BigQuery datatable. A particular focus is on accessing non-patent literature (NPL).

## Connect to Google Patents Public Datasets

```{r}
library(tidyverse)
library(DBI)
library(bigrquery)
con <- dbConnect(
  bigrquery::bigquery(),
  project = "cogent-tangent-279810"
)
```

Alternatively, you can also use the Google BigQuery web GUI to query the data. <https://console.cloud.google.com/bigquery?project=api-project-764811344545&p=patents-public-data&d=patents&t=publications_201912&page=table>


## Patents with citing non-patent literature

```{sql, connection = con}
SELECT e.country_code, COUNT(DISTINCT(e.publication_number)) as n_patents
FROM `patents-public-data.patents.publications_201912` as e, UNNEST(citation) as d
WHERE d.npl_text != ''
GROUP BY e.country_code
ORDER BY n_patents desc
```

### Sample Patents

```{sql, connection = con}
SELECT e.country_code, e.publication_number, d.npl_text
FROM `patents-public-data.patents.publications_201912` as e, UNNEST(citation) as d
WHERE d.npl_text like '%doi%' and country_code = 'EP'
LIMIT 10
```


```{sql, connection = con}
SELECT e.country_code, e.publication_number, d.npl_text
FROM `patents-public-data.patents.publications_201912` as e, UNNEST(citation) as d
WHERE e.application_number= 'US7527788'
LIMIT 10
```