---
title: "BQ Patent Open Data Detection"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

### Aim

The aim of this script is to retrieve all patents in Google Big Query where open data is cited.
For this purpose, we use keywords from the [Open Data Detection in Publications (ODDPub)]( https://github.com/quest-bih/oddpub), an R package available on GitHub

In particular, the oddpub following categories will be analyses:

- REPOSITORIES: Set of names of general-purpose repositories	
- GITHUB: Source code repository

We extend the list with patterns for pids

### Keywords per category

#### Generic repositories

```{r}
library(oddpub)
generic_repo <- oddpub:::.create_keyword_list()[["repositories"]] %>%
  stringr::str_remove_all("\\\\b|\\\\b") %>% 
  strsplit("|", fixed = TRUE) %>% 
  unlist()
generic_repo
```

#### Github

```{r}
github_repo <- oddpub:::.create_keyword_list()[["github"]] %>%
  stringr::str_remove_all("\\\\b|\\\\b") %>% 
  strsplit("|", fixed = TRUE) %>% 
  unlist()
github_repo
```

#### PIDs

```{r}
pids <- c("pmid",
  "pmcid", 
  #"doi", too large
  "rxiv")
```

### Call Big Query

Helper function

```{r}
library(DBI)
library(bigrquery)
library(glue)
con <- DBI::dbConnect(
  bigrquery::bigquery(),
  project = "api-project-764811344545"
)
# Search pattern in Big Query Patents NPL 
get_patents_with_repo <- function(repo_pattern) {
  
  my_pattern <- tolower(paste0('%', repo_pattern, '%'))
  
  req <- glue::glue_sql("
   SELECT
        e.publication_date,
        e.country_code,
        e.publication_number,
        e.family_id,
        d.npl_text,
        d.category
    FROM
        `patents-public-data.patents.publications` as e,
        UNNEST(citation) as d
    WHERE
<<<<<<< HEAD
        e.publication_date BETWEEN 20100101 AND 20203121
=======
        e.publication_date >= 20100101
>>>>>>> a4d75d7fc89b6a1b54b2d1d37ac8ba318f52f90d
        AND e.application_kind = 'A'
        AND lower(d.npl_text) like {tolower(paste0('%', my_pattern, '%'))}
  ", .con = con)
  out <- DBI::dbGetQuery(con, req)
  if(!is.null(out))
    dplyr::mutate(out, repo_pattern = repo_pattern)
}
```

Call 

```{r}
my_patterns <- c(
  #generic_repo, 
  github_repo, 
  pids)
npl_df <- purrr::map_df(my_patterns, get_patents_with_repo)
```

Basic stats

```{r}
npl_df %>%
  group_by(repo_pattern) %>%
  summarise(n = n_distinct(publication_number))
````

Export

```{r}
readr::write_csv(npl_df, "../data/npl_pattern.csv")
````
