---
title: "Quantify extraction success"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = TRUE
)
```


```{r}
library(tidyverse)

df <- read_csv("processed_data/extracted_references.csv")

```

There are two sets of references here: one including rich information 
(authors, article title, journal title, year, doi, issn, etc.) and one with
sparse data (abbreviated authors, abbreviated journal, volume, issue, year).

I have tried to separate them (the var short_cases denotes those with sparse
data), obviously not completely successfully.

Evaluation will take place within those subsamples.

# Sparse cases
In this group we have `r nrow(filter(df, short_cases))` cases.
```{r}
df %>% 
  filter(short_cases) %>% 
  select(authors, journal_title, volume, number, year) %>% 
  visdat::vis_miss()
```

# All other cases
In this group we have `r nrow(filter(df, !short_cases))` cases.
```{r}
df %>% 
  filter(!short_cases) %>% 
  select(authors, title, doi, issn, url, year) %>% 
  visdat::vis_miss()
```
